Heavy rainfall in Paraguay during the 2015-2016 austral summer: causes and sub-seasonal-to-seasonal predictive skill

### 2018-03-21 reports/writeup/paper.tex
Minor paper revisions

Inspection of \cref{fig:rain-wt} also suggests that at time scales of days to weeks, particular sequences of weather types tend to recur, and are associated with repeated rainfall storms.
The rainfall in late November 2015 occurred during \gls{wt} 1 and 4 days, with intermittent (and dry) \gls{wt} 5 occurrences.
During mid to late December 2015, \glspl{wt} 1 and 5 produced rainfall but the intermittent dry days were \gls{wt} 2.
During mid to late January 2016, \gls{wt} 3 led to persistent low rainfall.

>>>>

Inspection of \cref{fig:rain-wt} also suggests that at time scales of days to weeks, particular sequences of weather types tend to recur, and are associated with repeated rainfall storms.
From mid November to late December 2015, nearly all days were weather types 1, 4, and 5, consistent with the anticyclonic anomaly observed over central Brazil during that time (\cref{fig:anomalies}).
Nearly all of the heavy rainfall occurred during \glspl{wt} 1 and 4.
During mid to late January 2016, repeated \gls{wt} 3 days led to persistent low rainfall, and in mid February 2016 frequent occurrence of \gls{wt} 2 led to frequent, though generally not intense, rainfall.
